Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2021-09-22 doc/main_jfm.tex
editing section 4 complete

To reach consistent simulation outcomes, we first solve for a baseline JP vesicles 
that is suitably close to equilibrium. We start
with an assumed configuration of $N=58$ JP in the form of two, circular, apposing monolayers of about
$8$ nm in radius. 
Figure~\ref{figure2}a shows that the 
translational and rotational velocities vanish exponentially with
an approximate decay rate $\sim 4.6$ $\upmu$s$^{-1}$. An 
equilibrium configuration is therefore rapidly attained.
This equilibrium configuration serves as the initial data 
in the background flow simulations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tank-Treading Vesicles}
\begin{figure}
\begin{center}
\includegraphics[width=13.5cm]{Figure4_Wrapper.pdf}
%\hspace{-0.6cm}
%\includegraphics[height=2in]{ReducedArea.pdf}
%\hspace{0.6cm}
%\includegraphics[height=2in]{DecayRate.eps}\\
%\includegraphics[height=2in]{ArcLength.pdf}
%\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{\label{figure4}
 JP vesicles loose enclosed area and conserve length in shear flow. 
  Panel (a) gives the reduced area over time
  for four different shear rates. The smooth curves are a best-fit
  exponential curve. There is commensurate increase in excess length (panel (b)), 
  but the arc length of the mid plane curve is more or less constant.   
   The legend in panel (b) applies to panels (a)--(c).
  Panel (d) plots the steady-state reduced area and the decay rate $k$ (inset) using the exponential fit
  to the data in panel (a). }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
Our simulation studies begin by showing, for the first time, that a JP suspension with hydrophobic attraction 
behaves as a tank-treading vesicle
with zero viscosity contrast between the fluids inside and
outside of the vesicle (\cite{Finken08, Shaqfeh11}).
The centroid of the baseline $58$-body JP vesicle lies at the origin 
and the background shear flow 
\begin{align}
  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
\end{align} 
is applied for
shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
and $\mathbf{e}_y$ for the horizontal and vertical directions, respectively.
We use the dimensionless shear rate $\chi = \dot \gamma$ ns.

\begin{figure}
\begin{center}
\includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
\includegraphics[width=11cm]{Figure5B_Wrapper.pdf}
%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
%\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} 
  There is inter-monolayer slip present in the JP vesicle tank-treading motion at all shear rates.  
  Panel (a) tracks the angle  $\theta(t)$ between a pair of particles (blue and yellow) with respect to
  the JP vesicle centroid. The shear rate is $\chi=0.005$ and in the right figure, the yellow particle
  will complete two and quarter revolutions in the same time the blue particle completes two revolutions.
  The curves in panel (b) are the mean change in angle for various shear rates. 
  Slip velocity generally increases with shear rate but 
  we have marked two outliers (times symbols). }
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}
Another interesting flow to consider is the parabolic flow
\begin{align}
  \uu_\infty = v_{max}\left[ 1 - \left( 
    \frac{\xx \cdot \mathbf{e}_y}{wR_0}\right)^2
    \right]\mathbf{e}_x,
\end{align}
%
where $v_{max}$ is the flow strength and $w$ determines the shape of the
flow. $R_0$ is defined as the radius of the JP vesicle at $t=0$. The
behavior of a vesicle in this unbounded non-linear flow includes
vertical migration, and depending on the flow rate and reduced area, the
steady-state shape can be either a symmetric parachute or an asymmetric
slipper (\cite{Kaoui09, cou-kao-pod-mis2008, dan-vla-mis2009}).

@@

Figure~\ref{figure6} shows three configurations for one specific case
where the centroid of the JP vesicle is initially placed slightly
above the $x$-axis. The parameters are $v_{max} = 8.0$, $w=10$, and
$R_0=8$. The red curves are the midplanes and a particle pair is marked
in color. We observe that the deformed JP vesicle has a
counterclockwise movement and the shape of the vesicle approaches an
asymmetric slipper shape. Moreover, we observe inter-monolayer slip
between the two leaflets. For this test, the reduced area for this
configuration is approximately $0.9$ which matches the previous
numerical tests in~\cite{Kaoui09} where a slipper-like shape occurs when
the flow velocity is weak and the reduced area is large. A schematic of
the setup is shown in Figure~\ref{figure7} where the blue horizontal
line represents the mean $y$-position of all particles. The inset of
Figure~\ref{figure7} shows the trajectory of the mean position in the
$y$-direction that decreases towards $y=1$ for a period of time and then
starts to oscillate due to the granularity of the JP vesicle.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure6_Wrapper.pdf}
%\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle suspended in a parabolic flow
  where the strength of the flow is $v_{max}=32.8$~nm ns$^{-1}$, $R_0 =
  20$~nm, and the control parameter is $w=25$~nm. The configuration is
  the state when $t=\{0, 4000, 8000\}$ which correspond to $0\ \mu $s, $2.44\ \mu $s, and $4.88\ \mu $s. The red curves are the midplanes. Inter-monolayer slip is observed by comparing the relative  locations of the blue and yellow particles.}
\end{figure}

\begin{figure}
\centering
%\includegraphics[height=2in]{parabolic.eps}
  \caption{\label{figure7} The schematic of a JP vesicle suspended in a
  parabolic flow where the strength of the flow is
  $v_{max}=32.8$~nm~ns$^{-1}$, $R_0 = 20$~nm, and the control parameter
  is $w=25$~nm. The configuration occurs when $t=6.1\ \mu$s and red arrows indicate the tank-treading motion. The inset plots the trajectory of mean $y$-position over time.}
\end{figure}

@@

\subsection{Stretching and Permeability}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
%\includegraphics[height=2in]{relax2.eps}
%\includegraphics[height=2in]{relax.eps}\\
%\includegraphics[height=2.in]{N58_0pres.pdf}
%\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
\caption{\label{figure2} A JP Vesicle relaxing under a quiescent flow.
  (a) The blue dashed and solid curves are mean magnitudes of the
  particle velocities in $x$ and $y$ directions, respectively. The red
  curve shows the decreasing trend of the mean magnitude of particle
  orientation change. The black dashed line shows the reference of how
  all magnitudes decay. (b) Bilayer configurations for $t=0$ (black) and
  $t=1000$ (red) with particle directors. (c)--(d) show the fluid
  pressure profiles for $t=0$ and $t=1000$ where the background curves
  indicate the streamlines. In panel (c), the pressure value in internal
  fluid is much higher than the pressure outside of the bilayer. After
  the JP vesicle relaxes, this immersed permeable bilayer approaches the
  steady state shown in panel (d).}
\end{figure}

\begin{figure}
  \caption{\label{figure:permeability} JP vesicles are suspended in a
  quiescent flow for relaxations where the reference arc lengths $L_0$
  are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm,
  $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$
  decreases over time where the dashed curves represent the data and
  solid curves are linear fits; (b) A linear relationship between
  $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear
  relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels
  (b) and (c), the cross and asterisk symbols are numerical results and
  fitted by using solid lines.}
\end{figure}

Figures~\ref{figure2}c and~\ref{figure2}d demonstrate that the initial, non-equilibrium configuration has a large internal fluid pressure
that vanishes as the configuration tends toward the equilibrium state.  
This suggests that the initial collection of JP is under tension and
this tension is relaxed as fluid is expelled through the inter-particle
spacing. To make a comparison with membrane continuum mechanics, lipid
bilayer membranes have a large area modulus $K_A$ of about $240$ pN
nm$^{-1}$ \cite{NAGLE} and changes in surface area give rise to a
membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
membrane surface area and $A_0$ is the reference surface area in the
non-tensed state. In the two-dimensional vesicles, the tension becomes
\begin{align}
\label{eq:stretch}
\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
\end{align}
where $L$ and $L_0$ are the vesicle arc length and resting length,
respectively. A stretched, circular vesicles has a Laplace pressure 
\begin{align}
\label{eq:LaplacePressure}
\Delta p = \frac{\tilde \gamma}{R},
\end{align}
where $\Delta p$ is the difference in internal pressure to the pressure
at infinity and $R$ is the radius of the circular vesicle. The factor
$R^{-1}$ is the total curvature since the principle curvature in the
direction of the cylinder is zero.

The particles in our setup do not abut but rather have small gaps due to
repulsive forces. The gaps allow for some fluid flux across the JP
bilayer. In membrane mechanics, aqueous flux is quantified the equation
\begin{align}
  \label{eq:perm} 
  \frac{dA}{dt} = -P  L \Delta p,
\end{align}
where $P$ is a hydraulic permeability constant (\cite{chabanon2017,
qua-gan-you2021}).

The JP vesicle data is in complete agreement with the continuum
mechanical model~\eqref{eq:stretch}--\eqref{eq:perm}. In
Figure~\ref{figure:permeability}, we considered three configurations: a
configuration with 58 particles ($L_0 = 107$ nm, plus symbols); a
configuration with 119 particles ($L_0 = 218$ nm, asterisk symbols); and
finally a configuration with 117 particles but with diameter 1.25 nm
rather than the usual 2.5 nm ($L_0 = 141$ nm, times symbols). Here $A$
and $L$ refer to the area and length of the mid plane curve separating
the inner and outer monolayers. The values for $L_0$ are the asymptotic
values for $L$ in Figure~\ref{figure:permeability}c.

Figure~\ref{figure:permeability}a plots the data for the Laplace
pressure relationship \eqref{eq:LaplacePressure}. The pressure jump
$\Delta p$ is the pressure at the particle center minus the far-field
pressure (see Figures~\ref{figure2}c and~\ref{figure2}d), $R = L/2\pi$
is the vesicle radius, and the horizontal axis is the relative stretch.
The solid lines are linear fits, showing that for circular JP vesicles,
$R\Delta P$ is essentially proportional to the relative stretching
$L/L_0 - 1$. The proportionality constant is the same for the 58 and 119
particle cases where the diameters are the same, suggesting that the
stretching modulus $K_A$ of JP bilayers is independent of the number of
particles. The 117 particle case had diameters 1.25 nm and this data set
results in a smaller stretching modulus of $K_A = 102$~pN~nm$^{-1}$. The
interpretation is that changes to particle size, while keeping $\rho$,
$M$, and $\rho_0$ fixed, lead to different physical properties.

Furthermore, Figure~\ref{figure:permeability}b and shows that $L\Delta
P$ is proportional to $\frac{dA}{dt}$ in accord with \eqref{eq:perm}.
The slopes of the linear fits give the hydraulic permeability
coefficient $P$. The data provide $P = 0.0296$ nm$^3$ ns$^{-1}$
pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 58 and 119
particle cases, respectively. These values suggest that the JP bilayer
permeability is independent of particle number, as was the case for the
stretching modulus. The permeability for the 117 particle number is
0.0566 nm$^3$~ns$^{-1}$~pN$^{-1}$. The increase in the permeability is
caused by the hydrophobic attraction vanishing with particle size,
leading to larger gaps between the particles for the same repulsion. The
hydraulic permeability we calculate, however, is not in agreement with
experimentally derived values and is larger by a few orders of
magnitude. This discrepancy is perhaps due to inter-particle distance of
the JP being relatively large to the inter-molecular spacing of lipids
in real bilayers. In future studies, we can test this hypothesis be
changing the repulsion strength and length for example.

Since the vesicles in Figure~\ref{figure2}a are nearly circular, we can
combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
and~\eqref{eq:perm}, to derive
\begin{align}
\label{eq:perm_solution}
L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
\end{align}
The theoretical time courses for \eqref{eq:perm_solution} are in good
quantitative agreement with the JP data for
(Figure~\ref{figure:permeability}c).

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure9_Wrapper.pdf}
%  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{\label{figure9} The shape and trajectories of two
  JP vesicles suspended in a shear flow. The moving paths of the two
  centroids are plotted in blue and red. The centroids are initially
  located on the $x$-axis. For simulation time, $t = {0, 400,800,1200}$
  for (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).
  The fluid velocity profile is plotted in the background.
  }
\end{figure}

\begin{figure}
  \centering
\includegraphics[width=\textwidth]{Figure10_Wrapper.pdf}  
%\includegraphics[height=2in]{N116_shear_0.pdf}
%\includegraphics[height=2in]{N116_shear_2500.pdf}\\
%\includegraphics[height=2in]{N116_shear_5000.pdf}
%\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{\label{figure10} Two JP vesicles suspended in a shear flow
  where the dimensioneless shear rate is $\chi=0.005$. The initial
  configuration is shown in panel (a). Panels (b)-(d) represent configurations when $t = \{500, 1000, 1500\}$.
  The background color is the fluid
  pressure. The color bar is identical for all panels. Streamlines are
  plotted in purple. The insets of all panels are generated from
  simulations of a continuum model of the vesicles and the streamlines
  agree between the two models. }
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Shear Flow}

Figure~\ref{figure9} shows the simulation of two JP vesicles suspended
in a shear flow with shear rate $\chi=0.005$. We duplicate the
pre-relaxed $58$-body JP vesicle from previous sections to construct the
initial configuration shown in Figure~\ref{figure9}(a). The two centers
of mass are at $(-10,0)$ and $(10,0)$. In all panels, the blue and red
curves show the trajectory of the two JP vesicle centroids. They have
nearly completed a full period by $t=4000$. We also observe an adhesive
effect between the two JP vesicles that is set up by the hydrophobic
interactions and repulsive force. Similar dynamics have been observed
between a pair of adhering vesicles in a shear flow
(\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
behavior is absent when two JP vesicles are well-separated.

Snapshots of the fluid pressure are in Figure~\ref{figure10}. Since the
initial JP vesicles are pre-relaxed, there is initially no pressure jump
between the internal and external fluids (panel (a)). Panels (b)--(d)
show the configurations when $t = \{500,1000,1500\}$, and the
streamlines are plotted in the background for all panels. We include the
numerical results from a continuum model in all insets and these
comparisons give a qualitative agreement between two models.

\begin{figure}
\begin{center}
\includegraphics[width=0.97\textwidth]{Figure11_Wrapper.pdf}
%\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{\label{figure11} Two JP vesicles suspended in
  an extensional flow. The moving paths of the two centroids are plotted
  in blue in red. Each row corresponds to a different initial placement
  of the JP vesicles. The flow rate is $\chi = 0.005$ in all cases.
  (i) Both JP vesicle centroids are on the $x$-axis. (ii) The
  centroid of the left JP vesicle is $0.1$ units above the $x$-axis
  and the right JP vesicle is on the $x$-axis. (iii) The centroid of
  the left JP vesicle is $0.1$ units above the $x$-axis and the right
  JP vesicle is $0.1$ units below the $x$-axis. (iv) The centroid of
  the left JP vesicle is $0.5$ units above the $x$-axis and the
  centroid of the right JP vesicle is $0.5$ units below the $x$-axis.
  Figure~\ref{figure12} presents the numerical results from the case
  (iii).  The fluid velocity profile is plotted in the background.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Figure12_Wrapper.pdf}
%\includegraphics[height=2in]{N116_ext_0.pdf}
%\includegraphics[height=2in]{N116_ext_2000.pdf}\\
%\includegraphics[height=2in]{N116_ext_4000.pdf}
%\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{\label{figure12} Two JP vesicles suspended in an
  extensional flow where the dimensioneless extensional rate is
  $\chi=0.005$. The centroid of the left JP vesicle is $0.1$ units
  above the $x$-axis and the centroid of the right JP vesicle is
  $0.1$ units below the $x$-axis. The initial configuration is shown in
  panel (a). Panels (b)-(d) represent configurations when $t = \{400, 800, 1300\}$. 
  The background color is the fluid pressure. The color bar
  is identical for all panels. Streamlines are plotted in purple. The
  insets of all panels are generated from simulations of a continuum
  model of the vesicles and the streamlines agree between the models.}
\end{figure}

>>>>

To reach consistent simulation outcomes, we first solve for a baseline JP vesicles 
that is suitably close to equilibrium. We start
with an assumed configuration of $N=58$ JP in the form of two, circular, apposing monolayers of about
$8$ nm in radius. The 
translational and rotational velocities vanish exponentially with
an approximate decay rate $\sim 4.6$ $\upmu$s$^{-1}$. An 
equilibrium configuration is therefore rapidly attained.
This equilibrium configuration serves as the initial data 
in the subsequent background flow simulations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tank-Treading Vesicles}
\begin{figure}
\begin{center}
\includegraphics[width=13.5cm]{Figure4_Wrapper.pdf}
%\hspace{-0.6cm}
%\includegraphics[height=2in]{ReducedArea.pdf}
%\hspace{0.6cm}
%\includegraphics[height=2in]{DecayRate.eps}\\
%\includegraphics[height=2in]{ArcLength.pdf}
%\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{\label{figure4}
 JP vesicles loose enclosed area and conserve length in shear flow. 
  Panel (a) gives the reduced area over time
  for four different shear rates. The smooth curves are a best-fit
  exponential curve. There is commensurate increase in excess length (panel (b)), 
  but the arc length of the mid plane curve is more or less constant.   
   The legend in panel (b) applies to panels (a)--(c).
  Panel (d) plots the steady-state reduced area and the decay rate $k$ (inset) using the exponential fit
  to the data in panel (a). }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
Our simulation studies begin by showing, for the first time, that a JP suspension with hydrophobic attraction 
behaves as a tank-treading vesicle
%with zero viscosity contrast between the fluids inside and
%outside of the vesicle
(\cite{Finken08, Shaqfeh11}).
The centroid of the baseline $58$-body JP vesicle lies at the origin 
and the background shear flow 
\begin{align}
  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
\end{align} 
is applied for
shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
and $\mathbf{e}_y$ for the horizontal and vertical directions, respectively.
We use the dimensionless shear rate $\chi = \dot \gamma$ ns.

\begin{figure}
\begin{center}
\includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
\includegraphics[width=11cm]{Figure5B_Wrapper.pdf}
%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
%\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} 
  There is inter-monolayer slip present in the JP vesicle tank-treading motion at all shear rates.  
  Panel (a) tracks the angle  $\theta(t)$ between a pair of particles (blue and yellow) with respect to
  the JP vesicle centroid. The shear rate is $\chi=0.005$ and in the right figure, the yellow particle
  will complete two and a quarter revolutions in the same time the blue particle completes two revolutions.
  The curves in panel (b) are the mean change in angle for various shear rates. 
  Slip velocity generally increases with shear rate but 
  we have marked two outliers (times symbols). }
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}
Finally, we consider the parabolic background flow
\begin{align}
  \uu_\infty = v_{max}\left[ 1 - \left( 
    \frac{\xx \cdot \mathbf{e}_y}{wR_0}\right)^2
    \right]\mathbf{e}_x,
\end{align}
%
where $v_{max}$ is the flow strength and $w$ determines the shape of the
flow. The parameter $R_0$ is the radius of the JP vesicle at $t=0$ and 
$w$ sets the width of the profile.  
\cite{Kaoui09, cou-kao-pod-mis2008, dan-vla-mis2009} have shown that the
behavior of a vesicle in this unbounded  flow includes
vertical migration, and depending on the flow rate and reduced area, the
steady-state shape can be either a symmetric parachute or an asymmetric
slipper.

@@

Figure~\ref{figure6} shows four configurations for one specific case
where the centroid of the JP vesicle is initially placed slightly
above the $x$-axis.  We have marked a pair of particles blue and yellow
in the inner and outer leaflets, respectively,  and observe that the 
deformed JP vesicle (Figure~\ref{figure6}, $t = 12~\upmu$s) has a
counterclockwise movement and the shape of the vesicle approaches an
asymmetric slipper shape. For this test, the reduced area in the final
configuration is approximately $0.9$ which matches the previous
numerical tests in~\cite{Kaoui09} where a slipper-like shape occurs when
the flow velocity is weak and the reduced area is large.  The flow causes the 
vesicle, which is initially placed above the axis,
to draft downward where it reaches a steady height of about  $1$ nm.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure6_Wrapper.pdf}
%\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle placed in a parabolic flow drifts 
  toward the central axis.  It assumes a slipper shape and undergoes tank-treading
  like in the shear flow case.  The arrows on the left illustrate the background flow and 
  the arrows on the right show the velocity relative to the vesicle's moving frame. 
  The thick black curve plots the distance from the axis as a function of time from left to right.  
  The parameters are $v_{max} = 8$~nm ns$^{-1}$, 
  $w=10$, and $R_0=20$ nm.}
\end{figure}

@@

\subsection{Stretching and Permeability}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
%\includegraphics[height=2in]{relax2.eps}
%\includegraphics[height=2in]{relax.eps}\\
%\includegraphics[height=2.in]{N58_0pres.pdf}
%\includegraphics[height=2.in]{N58_5000pres.pdf}
%  \todo[inline]{Put pressure of each of the two configurations below
%  this.}
\caption{\label{figure2} 
  In JP vesicles, tension and pressure relax as fluid is expelled 
  through the particle interstices. 
  In panel (a), the thin curve plots the mean of the norm of the particle translational velocities.
  The thick curve plots the mean of the absolute value of the particle angular velocities.  
  At $t = 0$ $\upmu$s, the vesicle has a constant internal pressure 0.05~pN nm$^{-1}$ (red color, panel (b)).
  In panel (c),  pressure has dissipated and the vesicle has moved from its initial configuration (gray circles), to the equilibrium configuration
  (black circles).  The data in panels (d) and (e) support the linear relationship expressed by 
  \eqref{eq:LaplacePressure} and \eqref{eq:perm}.
  Circles are for a vesicle with 17 nm initial radius;
  square are for a 34 nm initial radius.  Asterisks are for 
  a 18 nm initial radius but with smaller, 1.25 nm diameter particles. 
  In panel (f), the theoretical time course  \eqref{eq:perm_solution} overlaps the data 
  using constants $K_A$ and $P$ derived from panels (d) and (e). }
\end{figure}
Finally, we show that the JP bilayer behaves as an extensible, permeable membrane. 
Figures~\ref{figure2}b shows an initial, non-equilibrium JP vesicle suspended in a quiescent flow $\uu_{\infty} = 0$.
The color map plots the pressure $p$. The red color in Figures~\ref{figure2}b 
shows a constant, positive internal pressure (0.05~pN nm$^{-1}$)
and the white shows a constant zero, external pressure.  
There is some fluid flow and the pressure vanishes as the configuration tends toward the equilibrium state (Figures~\ref{figure2}c).

What could be the source of this drop in pressure?
In continuum membrane mechanics, changes in surface area give rise to a
membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
membrane surface area and $A_0$ is the reference surface area in the
The area modulus $K_A$ of bilayers is about $240$ pN nm$^{-1}$ (\cite{NaTr00}).
In the two-dimensional vesicles, the tension becomes
\begin{align}
\label{eq:stretch}
\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
\end{align}
where $L$ and $L_0$ are the vesicle arc length and resting length,
respectively. Moreover, stretched, circular vesicles has a Laplace pressure 
\begin{align}
\label{eq:LaplacePressure}
\Delta p = \frac{\tilde \gamma}{R},
\end{align}
where $\Delta p$ is the difference in internal pressure to the pressure
at infinity, $R^{-1}$ is the total curvature of the circular cylinder.

Figure~\ref{figure2}c plots the data for the pressure jump
$\Delta p$ between the particle center and the far-field (see Figures~\ref{figure2}c and~\ref{figure2}d).
We use $R = L/(2\pi)$ for the vesicle radius, and the horizontal axis is the relative stretch.
The circles are data for a vesicle with radius 17 nm. The linear fit (solid lines) shows that 
$R\Delta P$ is proportional to the relative stretching $L/L_0 - 1$.
The squares are for a vesicle with twice the radius 34 nm, and the data overlap 
supports that the proportionality constant $K_A$ is a stretching modulus that is independent of vesicle size.
The data give $K_A = 170 \pm 9$ pN nm$^{-1}$ which is good agreement with the 
area moduli of lipid bilayer as determined by experiment. 
To evaluate how changes to particle size lead to different physical properties,
the asterisk symbols are for an 18 nm radius vesicle
consisting of particles with diameter 1.25 nm, instead of the usual 2.5 nm.
These data give smaller stretching modulus of $K_A = 102$~pN~nm$^{-1}$.

The particles in our setup do not abut but rather have small gaps due to
repulsive forces. The gaps allow for some fluid flux across the JP
bilayer, which can be quantified by the equation
\begin{align}
  \label{eq:perm} 
  \frac{dA}{dt} = -P  L \Delta p,
\end{align}
where $P$ is a hydraulic permeability constant (\cite{chabanon2017,
qua-gan-you2021}).
Figure~\ref{figure2}e shows that the data for 
$L\Delta p$ and $dA/dt$ obey the linear relationship expressed by \eqref{eq:perm}.
The slopes of the linear fits give the hydraulic permeabilities $P = 0.0296$ nm$^3$ ns$^{-1}$
pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 17 nm and 34 nm radius 
cases, respectively.   
Like  the area modulus, permeability is independent of vesicle size.
The hydraulic permeability we calculate, however, is not in agreement with
experimentally derived values and is larger by a few orders of
magnitude.

We suspect this discrepancy is due to inter-particle distance of
the JP being large compared to the inter-lipid spacing in real bilayers. To test this, we calculate the
permeability for the particles with diameter 1.25 nm. 
Due to their smaller size but fixed repulsion strength, these particles have a larger inter-particle spacing 
resulting in an increase in permeability, $P = 0.0566$~nm$^3$~ns$^{-1}$~pN$^{-1}$ (Figure \ref{figure2}e, asterisk symbols).

Since the vesicles in Figure~\ref{figure2}a are nearly circular, we can
combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
and~\eqref{eq:perm}, to derive
\begin{align}
\label{eq:perm_solution}
L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
\end{align}
The theoretical time courses for \eqref{eq:perm_solution} are in good
quantitative agreement with the JP data for
(Figure~\ref{figure2}f).

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure9_Wrapper.pdf}
%  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{\label{figure9} Two JP vesicles suspended in a shear flow
  interact by orbiting about the origin. The moving paths of the two
  centroids are plotted in blue and red. The centroids are initially
  located on the $x$-axis.  The fluid velocity streamlines appear in grey.
  The dimensionless shear rate is $\chi=0.005$.
  }
\end{figure}

\begin{figure}
  \centering
\includegraphics[width=\textwidth]{Figure10_Wrapper.pdf}  
%\includegraphics[height=2in]{N116_shear_0.pdf}
%\includegraphics[height=2in]{N116_shear_2500.pdf}\\
%\includegraphics[height=2in]{N116_shear_5000.pdf}
%\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{\label{figure10} 
  The figure is for the same simulation as in Figure~\ref{figure9}, 
  but also plots the fluid pressure $p$. The color bar is identical for all panels. 
  Internal pressure is initially zero, but then grows as the vesicles come close to contact  (panel (c)).
  The insets are generated from simulations of a continuum model of the vesicles (\cite{qua-vee-you2019}). 
  The streamlines of the two models are in agreement.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Shear Flow}
Finally, we can study vesicle-vesicle interactions in background flows. 
Figure~\ref{figure9} shows the simulation of two JP vesicles suspended
in a shear flow with shear rate $\chi=0.005$. We duplicate the
pre-relaxed $58$-body JP vesicle from previous sections and construct the
initial configuration shown in Figure~\ref{figure9}a. The two centroids
are at coordinates $(-25,0)$ and $(25,0)$ in nm. In all panels, the blue and red
curves show the trajectory of the two JP vesicle centroids. They have
nearly completed a full period by $t=4$ $\upmu$s.

We show snapshots of the fluid pressure in Figure~\ref{figure10}. Since the
initial JP vesicles are pre-relaxed, there is initially no pressure jump
between the internal and external fluids (panel (a)). Panels (b)--(d)
show the configurations when $t = \{0.5,1,1.5\}$ $\upmu$s, and the
streamlines are plotted in the background for all panels. 
We include the numerical results from a continuum model in all insets and these
comparisons give a qualitative agreement between two models.
We also observe an adhesive
effect between the two JP vesicles that is set up by the hydrophobic
attraction (Figure~\ref{figure10}c). Similar dynamics have been observed between a pair of adhering vesicles in a shear flow
(\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
behavior is absent when two JP vesicles are well-separated.

\begin{figure}
\begin{center}
\includegraphics[width=0.97\textwidth]{Figure11_Wrapper.pdf}
%\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{\label{figure11} 
  The initial placement of two JP vesicles suspended in
  an extensional flow affects the long-time dynamics.  
  The moving paths of the two centroids are plotted
  in blue in red. Each row corresponds to a different initial placement
  of the JP vesicles. 
  (i) Both JP vesicle centroids are on the $x$-axis. (ii) The
  centroid of the left JP vesicle is $0.25$ nm above the $x$-axis
  and the right JP vesicle is on the $x$-axis. (iii) The centroid of
  the left JP vesicle is $0.25$ nm above the $x$-axis and the right
  JP vesicle is $0.25$ units below the $x$-axis. (iv) The centroid of
  the left JP vesicle is $1.25$ nm above the $x$-axis and the
  centroid of the right JP vesicle is $1.25$ nm below the $x$-axis.
  The streamlines appear in grey and 
  the flow rate is $\dot \gamma =0.005$ ns$^{-1}$ in all cases.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Figure12_Wrapper.pdf}
%\includegraphics[height=2in]{N116_ext_0.pdf}
%\includegraphics[height=2in]{N116_ext_2000.pdf}\\
%\includegraphics[height=2in]{N116_ext_4000.pdf}
%\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{\label{figure12} The figure is for the simulation case (iii) of Figure~\ref{figure11},
  and additionally plots the pressure $p$.  The color bar is shared by all panels. 
  The insets of all panels are generated from simulations of a continuum
  model of the vesicles and the streamlines agree between the two models.}
\end{figure}
